CiteQ: Analysis on Citation Sentiment: University of Waterloo Computer Science Faculty Case Study

### 2024-04-03 paper/main.tex
up

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmlicensed}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{XXXXXXX.XXXXXXX}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation emai}{June 03--05,
  2018}{Woodstock, NY}
%%
%%  Uncomment \acmBooktitle if the title of the proceedings is different
%%  from ``Proceedings of ...''!
%%
%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%%  June 03--05, 2018, Woodstock, NY}
\acmISBN{978-1-4503-XXXX-X/18/06}

@@

@@

\received{20 February 2007}
\received[revised]{12 March 2009}
\received[accepted]{5 June 2009}

@@

\section{Methodology}
\subsection{Data Collection}
We used the Semantic Scholar (SS) API to collect the publication and citation data of all current (as of this writing) members of the University of Waterloo Computer Science faculty members. SS provides an API endpoint to retrieve the context of a citation. We used this endpoint to retrieve the citation context of each citation
made by a faculty member or to a faculty member. In total we collected data about 96 faculty members, 9,438 papers, and 697,609 citations. We formed an SQLite database, with the scheme shown in Figure \ref{fig:citeq-scheme}, to facilitate flexible querying of the data. This database is publicly available at \url{https://github.com/onurerenarpaci/citeQ.git}.

>>>>

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.

% \setcopyright{acmlicensed}
% \copyrightyear{2018}
% \acmYear{2018}
% \acmDOI{XXXXXXX.XXXXXXX}

%% These commands are for a PROCEEDINGS abstract or paper.

% \acmConference[Conference acronym 'XX]{Make sure to enter the correct
%   conference title from your rights confirmation emai}{June 03--05,
%   2018}{Woodstock, NY}

  %%
%%  Uncomment \acmBooktitle if the title of the proceedings is different
%%  from ``Proceedings of ...''!
%%
%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%%  June 03--05, 2018, Woodstock, NY}

% \acmISBN{978-1-4503-XXXX-X/18/06}

@@

\author{Yahya Jabary}
\email{yahya.jabary@uwaterloo.ca}
\affiliation{%
  \institution{University of Waterloo}
  \streetaddress{200 University Ave W}
  \city{Waterloo}
  \state{Ontario}
  \country{Canada}
  \postcode{N2L 3G1}
}

@@

% \received{20 February ???}
% \received[revised]{12 March ???}
% \received[accepted]{5 June ???}

@@

\section{Methodology}
\subsection{Data Collection}
We used the Semantic Scholar (SS) API to collect the publication and citation data of all current (as of this writing) members of the University of Waterloo Computer Science faculty members. SS provides an API endpoint to retrieve the context of a citation. We used this endpoint to retrieve the citation context of each citation
made by a faculty member or to a faculty member. In total we collected data about 96 faculty members, 9,438 papers, and 697,609 citations. We formed an SQLite database, with the scheme shown in Figure \ref{fig:citeq-scheme}, to facilitate flexible querying of the data. This database is publicly available at \url{https://github.com/sueszli/citeQ.git}.
